### 2019-03-17 papers/journal/intro.tex
update in intro

@@

\subsection{Combinatorial problem and use of Formal methods}
%
\ankit{A template: Requires complete rewriting}
The analysis of vesicle traffic systems is a difficult problem
because of the combinatorial scaling of possible traffic topologies and regulatory rules. 
%
For example, we might want to check some conjecture of interest for all graphs of a certain structure. 
%
The number of graphs with that specific structure with a combination of the possible regulatory rule will be large to handle by any tool.
%
Precise analysis of the properties of the VTS would be hindered by the same reason.

Previous analyses of vesicle traffic networks dealt with this combinatorial
explosion by using a sampling approach~\cite{mani2016stacking}. 
%
In these analyses, vesicle traffic is modelled as an update system. 
%
%The traffic rule specifies how the system transitions from one
%time point to the next. 
%
Given a traffic rule and an initial condition, the system is updates one step a time, updating molecular flux of the compartments, until a steady state is reached. 
%
The update rule defines the flux transition for the next step. 
%
By studying a large sample of randomly generated update rules, such analyses can make statistical claims about vesicle traffic. 
%

>>>>

A cell is a set of compartments exchanging molecules via vesicles of uniform size.
%
On the timescale of minutes, compartments are neither created nor destroyed, rather, they are in steady state. We assume that molecules are also neither created nor destroyed.
%
The identities of compartments and vesicles is encoded in their molecules, and identical vesicles fuse with identical target compartments.
%
Fusion of vesicles to compartments is driven by specific SNARE pairing, and a single active SNARE complex is necessary and sufficient for fusion.
%
The activity of a SNARE can be regulated by other molecules present on the same compartment or vesicle.

@@

\subsection{Combinatorial problem and use of Formal methods}
%
The analysis of vesicle traffic systems is a difficult problem
because of the combinatorial scaling of possible traffic topologies and regulatory rules. 
%
For example, we might want to check some conjecture of interest for all graphs of a certain structure. 
%
The number of graphs with that specific structure with a combination of the possible regulatory rule will be large to handle by any tool.
%
Precise analysis of the properties of the VTS would be hindered by the same reason.

In previous work, a sampling approach was undertaken. 
%
The study used a rule-based approach~\cite{mani2016stacking}, where given an initial condition of the cell, and rules for molecular traffic, the state of each compartment in the cell is updated until a steady state is reached. 
%
With this study, statistical claims can be made, but improbable albeit biologically possible solutions could have been missed.
%
Also, there are many ways in which the dynamics of vesicle transport can be played out, while a single one was explored in this work. 
%
It is possible that a different scheme for the dynamics could lead to a different set of solution

%Previous analyses of vesicle traffic networks dealt with this combinatorial
%explosion by using a sampling approach~\cite{mani2016stacking}. 
%
%In these analyses, vesicle traffic is modelled as an update system. 
%
%The traffic rule specifies how the system transitions from one
%time point to the next. 
%
%Given a traffic rule and an initial condition, the system updates molecular flux of the compartments one step a time choosing one among the possibly exponential choices of the rule.
%
%The update rule defines the flux transition for the next step. 
%
%This process is performed until a steady state is reached. 
%
%
%By studying a large sample of randomly generated update rules, such analyses can make statistical claims about vesicle traffic. 
%
